Generalized Plackett-Luce Likelihoods

### 2022-08-14 inst/jss_hyper3.Rnw
typos

Above, we see that Vadlejch has the highest estimated Bradley-Terry
strength, but further analysis with \code{equalp.test()} reveals that
there is no strong evidence in the datast to reject the hypothesis of
equal competitive strength ($p=0.26$), or that Vadlejch has a strength
higher than the null value of $\frac{1}{8}$ ($p=0.1$).

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  In Formula 1 Grand Prix, the
constructors' championship takes place between {\em manufacturers} of
racing cars (compare the drivers' championship, which is between
drivers).  In this analysis, the constructor is the object of
inference.  Each constructor typically fields two cars, each of which
separately accumulates ranking-based points at each venue.  Here we
use generalized Plackett-Luce to assess the contructors' performance.
The following table, included in the \code{hyper2} package as a
dataset, shows rankings for the first 9 venues of the 2021 season:

>>>>

Above, we see that Vadlejch has the highest estimated Bradley-Terry
strength, but further analysis with \code{equalp.test()} reveals that
there is no strong evidence in the dataset to reject the hypothesis of
equal competitive strength ($p=0.26$), or that Vadlejch has a strength
higher than the null value of $\frac{1}{8}$ ($p=0.1$).

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  In Formula 1 Grand Prix, the
constructors' championship takes place between {\em manufacturers} of
racing cars (compare the drivers' championship, which is between
drivers).  In this analysis, the constructor is the object of
inference.  Each constructor typically fields two cars, each of which
separately accumulates ranking-based points at each venue.  Here we
use generalized Plackett-Luce to assess the constructors' performance.
The following table, included in the \code{hyper2} package as a
dataset, shows rankings for the first 9 venues of the 2021 season:
